\begin{proof}
We need to show that any feasible solution to the full model $\model{\discretizationFull}$
is also feasible to the relaxation model $\model{\discretization, \itinSetSuper}$, and that the objective value is no worse in the relaxation.

The proof proceeds in three main steps. First, we prepare the necessary definitions and essential analytical tools. This includes introducing a routing existence lemma that disaggregates macroscopic flows into individual cyclic routes, and analyzing the core properties of the aggregation mapping $\Phi$ that globally govern the structural relationship between the original and partial time-space networks. Additionally, specific auxiliary sets and relations are defined to specifically tackle the intricacies of the resource availability constraints. Second, we explicitly construct a solution for the relaxation model $\model{\discretization, \itinSetSuper}$ from an arbitrary feasible solution of the full model $\model{\discretizationFull}$ by the mapping mentioned in the theorem statement \eqref{eq:map_ori2rel}. Finally, equipped with the preliminary tools, we verify that the constructed solution is feasible to $\model{\discretization, \itinSetSuper}$ and yields a non-worse objective value by examining each constraint and the objective function systematically.

\input{thm/valid_relaxation/prepare.tex}

With the preliminary tools in place, we now formally map an arbitrary feasible solution from the full model to the relaxed model.
Let $\bar{\solution}=(\bar{\fleetAssignVar}, \bar{\shareVar}, \bar{\outsideShareVar})$ be any feasible solution to $\model{\discretizationFull}$.

\paragraph*{Constructing solution in relaxation model}
We construct a solution $\solution = (\fleetAssignVar, \shareVar, \outsideShareVar)$ for $\model{\discretization, \itinSetSuper}$ from $\bar{\solution}$ by the mapping mentioned in the theorem statement \eqref{eq:map_ori2rel}. 
By construction $\fleetAssignVar_{af}\in\mathbb{Z}_{\ge0}$,
so the domain condition~\eqref{constr:relax.domain.x.flight} is satisfied.
All other variable-domain requirements remain unchanged and therefore continue to hold.

It remains to verify that this constructed solution satisfies all operational and choice constraints of $\model{\discretization, \itinSetSuper}$ and maintains a valid lower bound for the objective function. We evaluate these requirements systematically below.
\input{thm/valid_relaxation/assign_flow.tex}
\input{thm/valid_relaxation/assign_fleet_available.tex}
\input{thm/valid_relaxation/assign_cooldown.tex}
\input{thm/valid_relaxation/assign_seg_freq.tex}
\input{thm/valid_relaxation/choice_ratio.tex}
\input{thm/valid_relaxation/choice_limit.tex}
\input{thm/valid_relaxation/choice_capacity.tex}
\input{thm/valid_relaxation/choice_covering.tex}
\input{thm/valid_relaxation/revenue_preserve.tex}

Therefore for any feasible solution of the full model, there exists a feasible solution in the aggregated model with a non-inferior objective value, $\model{\discretization, \itinSetSuper}$ provides a valid lower bound.
\end{proof}
