\begin{proof}
    \newcommand{\assignmentVector}{\mathbf{x}}
    \newcommand{\feasibleSet}{\mathscr{X}}
    \newcommand{\vectorAdd}{\oplus }
    \newcommand{\vectorMinus}{\ominus}
    \newcommand{\vectorLe}{\preceq}
We fix a resource type $f\in\fleetSet$ and prove the statement for its assignment vector 
$\assignmentVector^f=\{\fleetAssignVar_{af}\}_{a\in\arcSet}$. $\assignmentVector^f_{a}$ denotes the number of resource type $f$ assigned to arc $a$, which is a non-negative real number.

\paragraph{Step 0. Algebraic structure.}
Define the flow feasible set denoting all assignment vectors satisfying the flow-balance constraint~\eqref{constr:main.flow}:
\[
\feasibleSet_f=\Bigl\{
\assignmentVector^f\in\mathbb{R}_{\ge0}^{\lvert\arcSet\rvert}\;\Bigm|\;
\sum_{a\in\outArcSet{i,t}}\assignmentVector^f_{a}-\sum_{a\in\inArcSet{i,t}}\assignmentVector^f_{a}=0,\ \forall(i,t)\in\nodeSet
\Bigr\}.
\]
\[
    \vectorAdd: \feasibleSet_f \times \feasibleSet_f \to \feasibleSet_f,\quad x \vectorAdd x' = \{x_a + x'_a\}_{a\in\arcSet}
\]
\[
    \vectorMinus: \feasibleSet_f \times \feasibleSet_f \to \feasibleSet_f,\quad x \vectorMinus x' = \{x_a - x'_a\}_{a\in\arcSet}
\]
\[
    \vectorLe: x \vectorLe x' \iff x_a \le x'_a,\ \forall a\in\arcSet
\]
$(\feasibleSet_f,\vectorAdd)$ forms a commutative monoid:
it is closed under addition $\vectorAdd$, associative, and admits the zero vector $\mathbf{0}$ as identity.
We equip it with the partial order $\vectorLe$ defined componentwise; for $x',x\in\feasibleSet_f$,
the difference $x\vectorMinus x'$ is defined if $x'\vectorLe x$ and remains in $\feasibleSet_f$.

\paragraph{Step 1. Cycle vectors.}
A \emph{directed cycle} $C=(a_1,\ldots,a_L)$ is a finite sequence of arcs 
forming a closed walk on $\net$; the same arc may appear multiple times along $C$.
For any arc $a\in\arcSet$, denote by
\[
    \nu_{C}(a) := \#\{r\in\{1,\ldots,L\}\mid a_r = a\}
\]
its multiplicity within $C$.
For any scalar $z\ge 0$, define its \emph{cycle vector}
\[
v(C;z)_a=
\begin{cases}
z\,\nu_{C}(a),& a\in C,\\[2pt]
0,&\text{otherwise}.
\end{cases}
\]
Then $v(C;z)\in\feasibleSet_f$ because every node on the cycle has one incoming and one outgoing arc,
and scaling by $z$ preserves the flow-balance constraint~\eqref{constr:main.flow}.

\paragraph{Step 2. Existence of a directed cycle.}
For a nonzero $\assignmentVector\in\feasibleSet_f$, define the positive-support subgraph 
${\net}^+(\assignmentVector)$ induced by $\arcSet^+(\assignmentVector)=\{a\in\arcSet\mid \assignmentVector_a>0\}$.
At every node of ${\net}^+(\assignmentVector)$, the flow-balance constraint ensures
$\text{outdegree}\ge1$ and $\text{indegree}\ge1$.
Starting from any node with positive outflow and following positive arcs,
finiteness of the network implies that a node must repeat, 
thus forming a directed cycle $C\subseteq \arcSet^+(\assignmentVector)$.

\paragraph{Step 3. Greedy peeling procedure.}
Let $z=\min_{a\in C}\assignmentVector_a/\nu_{C}(a)>0$ (so that $v(C;z)\vectorLe \assignmentVector$) and define $\assignmentVector':=\assignmentVector-v(C;z)$.
Then:
\begin{itemize}
\item $\assignmentVector'\ge0$ componentwise, because $z$ is the minimum scaled value $\assignmentVector_a/\nu_C(a)$;
\item $\assignmentVector'\in\feasibleSet_f$, since both $\assignmentVector$ and $v(C;z)$ satisfy~\eqref{constr:main.flow};
\item the support strictly shrinks: $\arcSet^+(\assignmentVector')\subsetneq \arcSet^+(\assignmentVector)$.
\end{itemize}
Therefore, for $\assignmentVector^f$ iterating this procedure finitely many times (at most $|A^+(\assignmentVector^f)|$)
yields a decomposition
\[
\assignmentVector^f=\sum_{k=1}^{K}v(C_k;z_k),\qquad K\le|A^+(\assignmentVector^f)|.
\]

\paragraph{Step 4. Constructing the routing plan.}
For each cycle $C_k$, let $\pathInRoute{f}{k}$ be its projection onto the set of service arcs
$\flightArc$.
Let $\routeAmount{\pathInRoute{f}{k}}:=z_k$, and denote
\[
    \nu_{fk}(a)
        := \#\{r\mid a_{k,r}=a\}
        = \nu_{C_k}(a),
\]
the number of times arc $a$ appears in the projected cycle (if $a\notin C_k$, the count is zero).
Then, for any $a\in\flightArc$,
\[
\sum_{k=1}^{K}\routeAmount{\pathInRoute{f}{k}}\nu_{fk}(a)
=\sum_{k=1}^{K}v(C_k;z_k)_a
=\assignmentVector^f_a
=\fleetAssignVar_{af},
\]
Define 
$\route{f}=\{(\pathInRoute{f}{k},\routeAmount{\pathInRoute{f}{k}})\}_{k=1}^{K}$
and 
$\routingPlan(\solution)=\{\route{f}\mid f\in\fleetSet\}$.
Hence, for every resource type $f$, we can derive a routing plan consistent with its assignment vector.
\end{proof}