\chapter{Conclusion}
\label{sec:conclusion}

Service network design with passenger choice is a fundamental problem in transportation planning that requires the simultaneous optimization of service operations and demand allocation under endogenous demand. The feedback loop between the service plan and passenger behavior---where the set of available itineraries determines demand, which in turn determines the profitability of the service plan---renders the problem computationally intractable for realistic instances. Standard approaches face fundamental limitations: direct MIP formulations overwhelm commercial solvers due to the massive number of itinerary variables and weak LP relaxations; Dynamic Discretization Discovery efficiently compresses the time-space network but lacks the mechanism to handle choice-based demand coupling; and decomposition heuristics that separate markets ignore the shared-capacity linkages that bind them together.

To address these challenges, we proposed the Itinerary Aggregation and Dynamic Refinement (\algoNotation), which extends DDD from the physical network dimension to the logical passenger dimension. The key algorithmic innovations are threefold. First, itinerary aggregation via path-signature-based super-itineraries eliminates the fictitious revenue that arises from fractional resource allocations in the relaxed network, producing a substantially tighter lower bound than the standard LP relaxation. Second, a structure-aware repair algorithm based on frequency fixing and itinerary cuts reconstructs feasible integer solutions from the relaxed lower-bound solution, yielding high-quality upper bounds. Third, a refinement strategy that detects and resolves three classes of relaxation artifacts---chronological violations, separation infeasibilities, and phantom revenue---guarantees finite convergence to the global optimum.

We validated the framework on a real-world airline scheduling instance encompassing 60 nodes, 259 directed segments, and 475,776 feasible itineraries. The \algoNotation algorithm closed the optimality gap to 0\% in under 11 hours, whereas the direct solver stalled at a gap of nearly 5\% after 12 hours with no further progress. Analysis of the optimal solution revealed profitability-driven market selectivity---the operator strategically serves only the most profitable subset of markets---and an efficient exploitation of connecting itineraries to consolidate fragmented demand across the network.

Several directions for future research emerge from this work. A natural extension is the application of the \algoNotation framework to other transportation modes where analogous choice-based service network design problems arise, including urban transit systems, intercity rail, and bus networks. Scaling the methodology to larger network instances with more nodes, segments, and service resource types remains an important computational challenge. Multi-day or multi-period planning horizons would capture temporal demand variation and enable more realistic operational planning. The integration of downstream operational constraints---such as crew scheduling and vehicle maintenance---into the service design model presents an opportunity to close the gap between strategic planning and day-of-operations feasibility. Finally, exploring alternative discrete choice models beyond the GAM/SBLP framework, as well as warm-starting strategies that transfer solution information across related problem instances, could further accelerate convergence and broaden the practical applicability of the approach.
