\MakeAbstract{
服务网络设计问题广泛存在于航空、铁路、城际客运以及其他定时服务运营场景中。经典服务网络设计通常将需求视为外生给定，并在离散化的时空网络上优化服务调度和资源分配；然而，在实际服务系统中，顾客会根据可用服务方案、出发时间、中转质量、旅行时间和价格等因素进行选择，使需求随服务计划内生变化。将选择行为纳入服务网络设计能够更准确地刻画供需相互作用，但也引入了大规模选择变量、选择一致性约束与资源调度约束之间的强耦合，使所得混合整数规划模型在实际规模下难以直接求解。传统基于时空网络离散化或动态细化的方法主要压缩物理服务网络，难以处理由顾客选择空间爆炸和时间聚合下虚假收入所带来的计算挑战。
为此，本文提出一种行程聚合与动态细化框架（\algoNotation）。该框架利用物理时空网络聚合后诱导的路径签名，将原始行程集合表示为紧凑的超级行程集合。与简单合并原始行程不同，本文为每个超级行程计算其所代表的原始行程组合吸引力总和的紧上界，并据此构造相应的收入上界。该聚合规则既保证超级行程能够覆盖原问题中的可行选择组合，避免松弛模型低估可行选择；又避免将同一聚合选择集内不可同时实现的原始行程收入简单累加，从而抑制时间聚合导致的虚假收入。基于这一超级行程表示，本文构造原问题最优值的双侧界：一方面，在聚合时空网络和超级行程空间上求解小规模松弛模型，快速获得有效下界；另一方面，利用松弛解给出的服务频率结构，并结合超级行程产生的有效收入层约束强化完整时空网络上的可行解修复模型，得到原问题可行解。当双侧界尚不能证明当前可行解的最优性时，本文有针对性地更新时空离散化及其诱导的超级行程表示，并证明该算法在有限次迭代内收敛到全局最优解。在大规模实例上的计算实验表明，\algoNotation 能够求解此前不可处理的、含百万级行程变量的大规模模型，并在实际可接受的计算时间内达到最优性容差。
}{服务网络设计，顾客选择，行程聚合，混合整数规划，精确算法}

\MakeAbstractEng{
Service network design with customer choice (\problemName) is prevalent in airlines, railways, intercity customer transport, and other scheduled service operations. Classical service network design treats demand as exogenously given and optimizes service scheduling and resource assignment on discretized time-space networks; however, in real service systems, customers choose among available service options based on departure times, connection quality, travel time, and fares, making demand endogenous to the service plan. Incorporating choice behavior into service network design captures supply-demand interactions more accurately, but introduces strong coupling among large-scale choice variables, choice-consistency constraints, and resource scheduling constraints, rendering the resulting mixed-integer program intractable at realistic scales. Traditional approaches based on time-space network discretization or dynamic refinement primarily compress the physical service network and cannot address the computational challenges arising from the explosion of the customer choice space and the fictitious revenue caused by temporal aggregation.

To this end, this paper proposes an Itinerary Aggregation and Dynamic Refinement framework (\algoNotation). The framework uses path signatures induced by physical time-space network aggregation to represent the original itinerary set as a compact set of super-itineraries. Unlike simple merging of original itineraries, this paper computes a tight upper bound on the combined attraction of feasible original itinerary combinations represented by each super-itinerary, and constructs corresponding revenue bounds. This aggregation rule ensures that super-itineraries cover all feasible choice combinations in the original problem, preventing the relaxation model from underestimating feasible choices; it also prevents simple accumulation of revenues from incompatible original itineraries within the same aggregated choice set, thereby suppressing fictitious revenue caused by temporal aggregation. Based on this super-itinerary representation, the paper constructs two-sided bounds on the optimal value of the original problem: on one hand, solving a compact relaxation model on the aggregated time-space network and super-itinerary space yields a valid lower bound; on the other hand, using the service frequency structure from the relaxation solution together with revenue-layer constraints derived from super-itineraries strengthens a feasible-solution repair model on the full time-space network, yielding feasible upper bounds. When the two-sided bounds cannot yet certify optimality of the current feasible solution, the paper updates the time-space discretization and its induced super-itinerary representation in a targeted manner, and proves that the algorithm converges to the globally optimal solution in a finite number of iterations. Computational experiments on large-scale instances demonstrate that \algoNotation\xspace solves previously intractable models with million-level itinerary variables, achieving the prescribed optimality tolerance within practical runtime limits.
}{Service Network Design, Customer Choice, Itinerary Aggregation, Mixed-integer Programming, Exact Algorithm}
